dispRity manual

### 2022-08-09 inst/gitbook/03_specific-tutorials.Rmd

```{r}
## Testing whether mean is dimension-level 1
if(make.metric(mean, silent = TRUE) != "level1") {
    message("The metric is not dimension-level 1.")
}
## Testing whether var is dimension-level 1
if(make.metric(var, silent = TRUE) != "level1") {
    message("The metric is not dimension-level 1.")
}
```

@@

par(mfrow = c(2,2))
## The preview plot with the tree using only defaults
plot(time_slices, type = "preview", specific.args = list(tree = TRUE))
## The same plot but by applying general options
plot(time_slices, type = "preview", specific.args = list(tree = TRUE),
     col = "blue", main = "General options")
## The same plot but by applying the colour only to the lines and change of shape only to the points
plot(time_slices, type = "preview", specific.args = list(tree = TRUE),
     lines.col = "blue", points.pch = 15, main = "Specific options")
## And now without the legend
plot(time_slices, type = "preview", specific.args = list(tree = TRUE),
     lines.col = "blue", points.pch = 15, legend = FALSE)
```

>>>>

```{r}
## Testing whether mean is dimension-level 1
if(make.metric(mean, silent = TRUE)$type != "level1") {
    message("The metric is not dimension-level 1.")
}
## Testing whether var is dimension-level 1
if(make.metric(var, silent = TRUE)$type != "level1") {
    message("The metric is not dimension-level 1.")
}
```

@@

par(mfrow = c(2,2))
## The preview plot with the tree using only defaults
plot(time_slices, type = "preview", specific.args = list(tree = TRUE))
## The same plot but by applying general options
plot(time_slices, type = "preview", specific.args = list(tree = TRUE),
     col = "blue", main = "General options")
## The same plot but by applying the colour only to the lines
## and change of shape only to the points
plot(time_slices, type = "preview", specific.args = list(tree = TRUE),
     lines.col = "blue", points.pch = 15, main = "Specific options")
## And now without the legend
plot(time_slices, type = "preview", specific.args = list(tree = TRUE),
     lines.col = "blue", points.pch = 15, legend = FALSE)
```

### 2022-08-09 inst/gitbook/index.Rmd

```{r, eval = TRUE, echo = FALSE}
## master version
version_raw <- RCurl::getURL("https://raw.githubusercontent.com/TGuillerme/dispRity/master/DESCRIPTION")
version_master <- strsplit(strsplit(version_raw, split = "Version: ")[[1]][2], split = "\nDate:")[[1]][1]
version_master <- 1.6

## release version
version_raw <- RCurl::getURL("https://raw.githubusercontent.com/TGuillerme/dispRity/release/DESCRIPTION")
version_release <- strsplit(strsplit(version_raw, split = "Version: ")[[1]][2], split = "\nDate:")[[1]][1]
version_release <- 1.6

## CRAN version
version_raw <- RCurl::getURL("https://cran.r-project.org/web/packages/dispRity/index.html")
version_CRAN <- strsplit(strsplit(version_raw, split = "\n<td>Version:</td>\n<td>")[[1]][2], split = "</td>\n</tr>\n<tr>\n<td>Depends:")[[1]][1]
version_CRAN <- 1.6
```

>>>>

```{r, eval = TRUE, echo = FALSE}
## master version
version_raw <- RCurl::getURL("https://raw.githubusercontent.com/TGuillerme/dispRity/master/DESCRIPTION")
version_master <- strsplit(strsplit(version_raw, split = "Version: ")[[1]][2], split = "\nDate:")[[1]][1]
version_master <- 1.7

## release version
version_raw <- RCurl::getURL("https://raw.githubusercontent.com/TGuillerme/dispRity/release/DESCRIPTION")
version_release <- strsplit(strsplit(version_raw, split = "Version: ")[[1]][2], split = "\nDate:")[[1]][1]
version_release <- 1.7

## CRAN version
version_raw <- RCurl::getURL("https://cran.r-project.org/web/packages/dispRity/index.html")
version_CRAN <- strsplit(strsplit(version_raw, split = "\n<td>Version:</td>\n<td>")[[1]][2], split = "</td>\n</tr>\n<tr>\n<td>Depends:")[[1]][1]
version_CRAN <- 1.7
```
